Context-dependent consequences of including lagged effects in demographic models

### 2022-05-24 docs/paper.Rmd
make html look better

institute:
  - UF_WEC: Department of Wildlife Ecology and Conservation, University of Florida, Gainesville, Florida 32611-0430
  - UF_LAS: Center for Latin American Studies, University of Florida, Gainesville, Florida 32611-5530  
  - BDFFP: Biological Dynamics of Forest Fragments Project, INPA-PDBFF, CP 478, Manaus, Amazonas 69011-970 Brazil
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      linenumbers: yes
      number_sections: no
      fig_caption: yes
      reference_docx: "templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=templates/scholarly-metadata.lua
      - --lua-filter=templates/author-info-blocks.lua
      #- -Fpandoc-crossref #required for cross-ref equations
linkcolor: blue
bibliography: references.bib
csl: "templates/the-american-naturalist.csl" # Insert path for the bib-style
keywords: |
  integral projection models; environmental stochasticity; lagged effects
highlights: |
  These are the highlights

>>>>

institute:
  - UF_WEC: Department of Wildlife Ecology and Conservation, University of Florida, Gainesville, Florida 32611-0430
  - UF_LAS: Center for Latin American Studies, University of Florida, Gainesville, Florida 32611-5530  
  - BDFFP: Biological Dynamics of Forest Fragments Project, INPA-PDBFF, CP 478, Manaus, Amazonas 69011-970 Brazil
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      linenumbers: yes
      number_sections: no
      fig_caption: yes
      reference_docx: "templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=templates/scholarly-metadata.lua
      - --lua-filter=templates/author-info-blocks.lua
      #- -Fpandoc-crossref #required for cross-ref equations
    bookdown::html_document2: 
      theme: 
        version: 4
        bootswatch: journal
      number_sections: no
      fig_caption: yes
      pandoc_args:
      - --lua-filter=templates/scholarly-metadata.lua
      - --lua-filter=templates/author-info-blocks.lua
linkcolor: blue
bibliography: references.bib
csl: "templates/the-american-naturalist.csl" # Insert path for the bib-style
keywords: |
  integral projection models; environmental stochasticity; lagged effects
highlights: |
  These are the highlights
